Clouds and Radiation in a mock-Walker Circulation

### 2020-09-11 Silvers_WalkerCell_revision.tex
further changes to Silvers_WalkerCell_revision.tex and Silvers_WalkerCell_response2reviewers.tex in the revisions of the WalkerCirculation paper.  This commit is just before I attempt to break section 3 into two subsections.

%\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
%\usepackage[finalnew]{trackchanges}   % use this to create the final pdf without the changes shown.
\usepackage{soul}
\linenumbers

@@

\begin{itemize}
  \item {An increase of $\overline{\rm{P}}$  for the P100,P25 and E25 experiments.}
  \item {A decrease of $\overline{\rm{P}}$  for the E1 and E2 experiments.}
  \item {The horizontally oriented low-level circulations strengthen, and the regions of high precipitation are more concentrated  
  in geographic space (Figures \ref{fig:rh_psi_P25vsE25}, \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).  }
  \item {The surface enthalpy flux decreases by tens of $\rm{W m^{-2}}$ and is much more variable among the models over the warm patch (Figure \ref{fig:enthalpy} a).}
  \item {The spatial gradients of $\theta_e$ (Figure \ref{fig:enthalpy} b), the specific humidity, temperature, and virtual temperature 
  (not shown) increases on the lowest atmospheric level.  }
 \item {\remove[LGS]{When convection is parameterized the total domain mean condensate increases at all heights 
  (Figure 6), in contrast to when the convection is explicit and 
  the condensate aloft decreases (Figure 11.}    }
\end{itemize}

>>>>

%\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges}        % for track changes. finalnew option will compile document with changes incorporated.
%\usepackage[finalnew]{trackchanges}   % use this to create the final pdf without the changes shown.
\usepackage{soul}
\linenumbers

@@

\begin{itemize}
  \item {An increase of $\overline{\rm{P}}$  for the P100,P25 and E25 experiments.}
  \item {A decrease of $\overline{\rm{P}}$  for the E1 and E2 experiments.}
  \item {The horizontally oriented low-level circulations strengthen, and the regions of high precipitation are more concentrated  
  in geographic space (Figures \ref{fig:rh_psi_P25vsE25}, \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).  }
  \item {The surface enthalpy flux decreases by tens of $\rm{W m^{-2}}$ and is much more variable among the models over the warm patch (Figure \ref{fig:enthalpy} a).}
  \item {The spatial gradients of $\theta_e$ (Figure \ref{fig:enthalpy} b), the specific humidity, temperature, and virtual temperature 
  (not shown) increases on the lowest atmospheric level.  }
 {\remove[LGS]{When convection is parameterized the total domain mean condensate increases at all heights 
  (Figure 6), in contrast to when the convection is explicit and 
  the condensate aloft decreases (Figure 11.}    }
\end{itemize}
